Two measures are better than one: Combining iconicity ratings and guessing experiments for a more nuanced picture of iconicity in the lexicon

### 2022-01-30 paper.Rmd
version of R markdown which has the iconicity box code at the end

>>>>

```{r}
oppres%>%
  rename(guessing_accuracy=score)%>%
  left_join(othersratings,by="identifier")->t

t%>%
  ggplot(aes(x=mean_rating,y=guessing_accuracy))+geom_point()->plot

ggplotly(plot)

classify <- function(score){
  if (score<0.5){return(1)}
  else if(score<0.75){return(2)}
  else{return(3)}
}

othersratings%>%
  arrange(mean_rating)%>%
  rowid_to_column()%>%
  mutate(quartile=rowid/304)%>%
  rowwise()%>%
  mutate(rating_score=classify(quartile))->ratings_transformed

guess_classify <- function(score){
  if (score<=1/3){return(NA)}
  else if(score<2/3){return(1)}
  else if(score<5/6){return(2)}
  else{return(3)}
}

oppres%>%
  rowwise()%>%
  mutate(guess_score=guess_classify(score))->guesses_transformed

thing <- inner_join(guesses_transformed,ratings_transformed,by="identifier")%>%drop_na()

table(thing$guess_score,thing$rating_score)

thing%>%
  rowwise()%>%
  mutate(form=str_split(identifier,"_")[[1]][1])%>%
  left_join(info,by="form")%>%
  mutate(random_x=runif(min=1,max=4,n=1))%>%
  mutate(random_y=runif(min=1,max=4,n=1))%>%
  ggplot(aes(x=random_x,y=random_y,label=identifier,colour=ideophone))+facet_grid(guess_score~rating_score)+geom_jitter()+geom_text_repel()->plot
p <- ggplotly(plot)
p
htmltools::save_html(
  html = htmltools::as.tags(
    x = plotly::toWebGL(p),
    standalone = TRUE),
  file = "test.html")
htmlwidgets::saveWidget(p,"test.html")
```
